The Astropy Project

### 2017-11-13 main.tex
more future

\subsection{Future versions of the \astropypkg core package}

@@

\par In the next major release after v3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation. To prepare for this release, software for testing and
monitoring the performance of the code are being developed.   Less
functionality may be introduced in this release while the focus will be
primarily on improved performance.  In addition, a new suite of tutorials
and documentation are being prepared for this release.
%
\par Beyond the core code, the \astropy project is also further
developing the affiliated packages.  This includes elevating a suite of
packages into part of the core project. While these may not be integrated
into the \astropypkg core code, these projects provide code that is
useful to the astronomical community and meet the testing and
documentation standards of \astropy.   Some of these new efforts includes
an initiative to develop tools for spectroscopy
\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX
projection% \citep{astropy-healpix}
.
\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}

>>>>

\subsection{Future versions of the \astropypkg core and affiliated packages}

@@

In the next major release after version 3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.

Beyond the core code, the \astropy project is also further developing the
\astropy-managed affiliated packages.
While these may not be integrated into the \astropypkg core package, these
projects provide code that is useful to the astronomical community and meet the
testing and documentation standards of \astropy.
Some of these new efforts includes an initiative to develop tools for
spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX
projection. %\citep{astropy-healpix}
\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
